---
title: "Project of Practical Machine Learning"
author: "Frank"
date: "February 22, 2015"
output: html_document
---


## Define the question 

### Data 

The data is about:
+ Recording movement of the belt, forearm, arm, and dumbell 
+ 6 participants. 

They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). 

### Data preprocess
First read the data:
```{r}
testing <-read.csv("pml-testing.csv",header = T,na.strings = c("", " ","NA"))
training <- read.csv("pml-training.csv",header = T,na.strings = c("", " ","NA"))
testing<- testing[,c(-1,-2)];training<-training[,c(-1,-2)]
dim(training);dim(testing)
```

And then clean the data (delete the col with NA.) 
```{r}
idx <- !apply(training, 2, function(x) any(is.na(x)))
training <- training[, idx] 
testing <- testing[,idx]
dim(training);dim(testing)
```

Make all the feature (except "class") numeric. 
```{r}
testing[,-58] <- sapply(testing[,-58],as.numeric)
training[,-58] <- sapply(training[,-58],as.numeric)
```

### Data slice 
Use caret package, devide the training data into: train set and test set: 
```{r}
library(caret)
inTrain <- createDataPartition(y=training$classe, p=0.7, list=FALSE)
ttrain <- training[inTrain,]
ttest <- training[-inTrain,]
```

## Machine learning

### Use ttrain set to train the random forest model 

Construct a random forest model for all the 57 features to predict "classes". Trained the model by the ttrain set. 

```{r,cache=TRUE}
library(randomForest)
library(caret)
# use random Foreset method 
modFit1<-randomForest(formula = classe ~ ., data = ttrain, ntree = 500) 
```

### Cross validate the model's prediction by using ttest set. 
```{r,cache=TRUE}
# compare test set
predTest<-predict(modFit1,ttest)
(tab<-confusionMatrix(predTest, ttest$classe)$table)
```

The error rate is: 
```{r}
1-sum(diag(tab))/sum(tab)
```

## Predict the 20 testing data set
```{r,cache=TRUE}
# use in the real test 
predtest <- predict(modFit1,testing[,-58])
predtest

```

## Submit the results

```{r,eval=FALSE}
answers =as.character(predtest)
```

then you can load this function by copying and pasting it into R:

```{r,eval=FALSE}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
```

** create a folder where you want the files to be written**. Set that to be your working directory and run:
 
```{r,eval=FALSE}
pml_write_files(answers)
```



